How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 2 Response/Ref2.tex
NM

\noindent
It does not seem odd to us. Varying the number of bodies, $M$, is one way (perhaps the best way) to alter the permeability while keeping the porosity fixed. In the study of porous media, considerable attention is given to characterizing both a medium's porosity and it's permeability, as these two properties can change independent of one another due to microstructure. Studying few instances of small $M$ would not permit us to study more instances of large $M$ since the computational time required for the large-$M$ simulations is so much larger.

>>>>

\noindent
It does not seem odd to us. Varying the number of bodies, $M$, is one way (perhaps the best way) to alter the permeability of a medium while keeping it's porosity fixed. In the study of porous media, considerable attention is given to characterizing both a medium's porosity and it's permeability, as these two properties can be altered independently by altering the microstructure. Studying fewer instances of small $M$ would not permit us to study more instances of large $M$ since the computational time required for the large-$M$ simulations is so much larger.

We remark that one key discovery we made was the late surge in configurational anisotropy for simulations featuring a large number of bodies, $M \ge 60$, and how this connects to channelization. Had we not varied $M$, we could not have discovered the threshold of 60 required for this phenomenon.
\\ \\

\noindent \comment{Reviewer \#2: 
In addition, I found a few typos as I read:
\\ }
